NMRlipids IV: Headgroup \& glycerol backbone structures, and cation binding in bilayers with PS lipids

### 2018-08-07 Manuscript/manuscriptPS.tex
Update authors
Add authors
Update GROMOS-CKP results into the manuscript

\author{Tiago M. Ferreira}
\affiliation{Halle, Germany}
\author{Matti Javanainen}
\affiliation{Institute of Organic Chemistry and Biochemistry,
Academy of Sciences of the Czech Republic, 
Prague 6, Czech Republic}
\author{Markus Miettinen}
\affiliation{Potsdam, Germany}
\author{Josef Melcr}
\affiliation{Institute of Organic Chemistry and Biochemistry,
Academy of Sciences of the Czech Republic, 
Prague 6, Czech Republic}
\author{O. H. Samuli Ollila  \todo{Authorlist is not yet complete}}
\email[]{samuli.ollila@helsinki.fi}
%\homepage[]{Your web page}
\affiliation{Institute of Organic Chemistry and Biochemistry,
Academy of Sciences of the Czech Republic, 
Prague 6, Czech Republic}
\affiliation{Institute of Biotechnology, University of Helsinki}
%\author{NMRlipids collaboration}
%\affiliation{nmrlipids.blogspot.fi}

@@

@@

\begin{figure*}[]
  \centering
  \includegraphics[width=16.0cm]{../Figs/HGorderparametersPCvsPS.eps}
  \caption{\label{HGorderparametersPCvsPS}
    Changes of PC (left panel) and PS (right panel) headgroup order parameters
    from POPC:POPS mixtures with increasing amount of POPS.
    Experimental results of POPC are taken from Ref. \citenum{scherer87}
    (signs are determined as discussed in \cite{botan15,ollila16}).
    Experimental values for POPS in pure bilayer and in mixture are  
    measured in this work and in Ref. \citenum{roux90} at 298K, respectively.
    Since the experimental data of POPS in pure and diluted mixture come from
    different experimental sets (13C NMR in this work and 2H NMR from Ref. \citenum{roux90}),
    the experimental change of the order parameter is less accurate than in typical measurements
    where same technique is used in all conditions, see discussion about qualitative and quantitative 
    accuracy in Ref. \citenum{ollila16}.
    For POPC (left panel) the zero point of y-axis is set to the value of pure bilayer.
    For $\beta$-carbon of POPS (right panel, top) the zero point of y-axis is
    set to the value from POPC:POPS (5:1) mixture.
    For $\alpha$-carbon of POPS (right panel, bottom) the y-axis is tranferred
    with the same value for both order parameters such that the lower order
    parameter value from POPC:POPS (5:1) mixture is at zero
    to correctly illustrate the significant forking.
  }
  \todo{Simulation of CHARMM36 at 298K should be maybe rerun with Gromacs 5.} \\
  \todo{Simulation of pure POPC at 298K with Lipid14 would be useful for this plot (only at 303 K is available from NMRlipids I)} \\
  \todo{MacRog simulations of pure POPS with potassium counterions only would be useful for this and other plots.} \\
  \todo{The data for Gromos-CKP by Tom Piggot: http://nmrlipids.blogspot.com/2017/03/nmrlipids-iv-headgroup-glycerol.html?showComment=1528213129976\#c8319083196182661431
    should be added into the plot.}
\end{figure*}

>>>>

\author{Tiago M. Ferreira}
\affiliation{Halle, Germany}
\author{Ivan Gushchin}
\affiliation{Moscow Institute of Physics and Technology}
\author{Matti Javanainen}
\affiliation{Institute of Organic Chemistry and Biochemistry,
Academy of Sciences of the Czech Republic, 
Prague 6, Czech Republic}
\author{Batuhan Kav}
\affiliation{Potsdam, Germany}
\author{Jesper J. Madsen}
\affiliation{Department of Chemistry, The University of Chicago, Chicago, Illinois 60637, United States of America}
\author{Markus Miettinen}
\affiliation{Potsdam, Germany}
\author{Josef Melcr}
\affiliation{Institute of Organic Chemistry and Biochemistry,
Academy of Sciences of the Czech Republic, 
Prague 6, Czech Republic}
\author{O. H. Samuli Ollila}
\email[]{samuli.ollila@helsinki.fi}
%\homepage[]{Your web page}
\affiliation{Institute of Organic Chemistry and Biochemistry,
Academy of Sciences of the Czech Republic, 
Prague 6, Czech Republic}
\affiliation{Institute of Biotechnology, University of Helsinki}
\author{Thomas Piggot   \todo{Authorlist is not yet complete}}
\affiliation{Southampton, United Kingdom}
%\author{NMRlipids collaboration}
%\affiliation{nmrlipids.blogspot.fi}

@@

    POPC:POPS (5:1)/Na$^+$  & GROMOS-CKP \cite{??}             &0    & 0     & 110:22 & ?     & 0  & 298  & 500 & 100 & \cite{POPCpopsGROMOSCKPwithNa}  \\
    POPC:POPS (5:1)/Na$^+$  & GROMOS-CKPM \cite{??}            &0    & 0     & 110:22 & ?     & 0  & 298  & 500 & 100 & \cite{POPCpopsGROMOSCKPMwithNa}  \\

@@

\begin{figure*}[]
  \centering
  \includegraphics[width=16.0cm]{../Figs/HGorderparametersPCvsPS.eps}
  \caption{\label{HGorderparametersPCvsPS}
    Changes of PC (left panel) and PS (right panel) headgroup order parameters
    from POPC:POPS mixtures with increasing amount of POPS.
    Experimental results of POPC are taken from Ref. \citenum{scherer87}
    (signs are determined as discussed in \cite{botan15,ollila16}).
    Experimental values for POPS in pure bilayer and in mixture are  
    measured in this work and in Ref. \citenum{roux90} at 298K, respectively.
    Since the experimental data of POPS in pure and diluted mixture come from
    different experimental sets (13C NMR in this work and 2H NMR from Ref. \citenum{roux90}),
    the experimental change of the order parameter is less accurate than in typical measurements
    where same technique is used in all conditions, see discussion about qualitative and quantitative 
    accuracy in Ref. \citenum{ollila16}.
    For POPC (left panel) the zero point of y-axis is set to the value of pure bilayer.
    For $\beta$-carbon of POPS (right panel, top) the zero point of y-axis is
    set to the value from POPC:POPS (5:1) mixture.
    For $\alpha$-carbon of POPS (right panel, bottom) the y-axis is tranferred
    with the same value for both order parameters such that the lower order
    parameter value from POPC:POPS (5:1) mixture is at zero
    to correctly illustrate the significant forking.
  }
  \todo{Simulation of CHARMM36 at 298K should be maybe rerun with Gromacs 5.} \\
  \todo{Simulation of pure POPC at 298K with Lipid14 would be useful for this plot (only at 303 K is available from NMRlipids I)} \\
  \todo{MacRog simulations of pure POPS with potassium counterions only would be useful for this and other plots.} \\
  \todo{The data from POPC used in Gromos-CKP by would be useful for this plot.}
\end{figure*}
